### 2019-08-05 Thesis/pages/design.tex
Changes; - Added implementation details - Added some results write ups for the first experiment

\section{Design of GreenOnion}
To answer Research Questions \ref{goal:complexity} and \ref{goal:hardwareRequired} fully, it is necessary to implement an actual code base that will be used to generate actual keys.

@@

\subsection{Metric performance}
In order to answer Research Question \ref{goal:bestMetrics} and reduce the number of metrics to asses in the later rounds, the performance of similarity metrics required comparison. The thinning out of metrics is required due to limited resources and, therefore, possible further work could involve repeating this work with a much more varied selection of metrics. As explained in a previous section (See Section \ref{sec:metrics}) the chosen metrics up for assessment are Soundex, Metaphone, NYSIIS, Levenshtein and Phonetic vectors.

@@

@@

>>>>

\section{Design of GreenOnion}
\label{sec:greenDesign}
To answer Research Questions \ref{goal:complexity} and \ref{goal:hardwareRequired} fully, it is necessary to implement an actual code base that will be used to generate actual keys.

@@

\subsection{Metric performance}
\label{exp:metric}
In order to answer Research Question \ref{goal:bestMetrics} and reduce the number of metrics to asses in the later rounds, the performance of similarity metrics required comparison. The thinning out of metrics is required due to limited resources and, therefore, possible further work could involve repeating this work with a much more varied selection of metrics. As explained in a previous section (See Section \ref{sec:metrics}) the chosen metrics up for assessment are Soundex, Metaphone, NYSIIS, Levenshtein and Phonetic vectors.

@@

\subsubsection{Considerations}
This section will discuss the considerations required when interpreting the results of the study.

The first consideration is the way the words are compared. Due to the channel of authentication being phone based the comparison of words will be a mixture of auditory and textual. This is because a user needs to match a words sound to the one displayed on their device. In the case of this experiment the users are asked to compare the sound of two word that are visually displayed to them. Therefore, this experiment does not fully capture the targeted scenario. This was decided partly to aforementioned lack of resources. The main design of the experiment was to provide a simple way to cull the large number of metrics. The initial choice of five metrics discussed in Section \ref{sec:metrics} was to be followed by a more empirical decision. Further work, therefore, could improve by producing more conclusive results on the performance of the metrics.

Another consideration is the demographics of people accessible on Mechanical Turk. A comprehensive and still active survey run by D Difallah \textit{et al.} \cite{difallah2018demographics} shows that MTurk workers are younger and have a larger household income than that of the US population. This has to be taken into consideration when interpreting the results because it will inherently introduce a bias. This is due to the assumptions that an increase in age provides a better understanding of more obscure words, and, therefore, a better representation of the metrics performance over the entire dictionary.

@@

\subsubsection{Considerations}
\textbf{TODO}

Demographics of MTurk workers (Discussed in the previous section)

### 2019-08-05 Thesis/pages/experiments.tex
Changes; - Small changes made to the main experiment - Updated lists of vuln keys - Added more content to the thesis
Changes; - Added implementation details - Added some results write ups for the first experiment

\section{Experiment 1}
% Methodology
% Demographic
% Results

@@

>>>>

\section{Metric Performance - Results}
As discussed in Section \ref{exp:metric} the goal of the experiment was the cull the number of metrics to be assessed in the following experiment. This section will discuss the demographics of participants alongside the subsequent results

\begin{table}[h!]
    \centering
    \begin{tabular}{|l|ll|}
        \hline
        Gender & Male: & 46.2\% \\
               & Female: & 53.8\% \\
        \hline
        Age:   & 18-24: & 10.6\% \\ 
               & 25-29: & 20.2\% \\ 
               & 30-39: & 30.8\% \\ 
               & 40-49: & 22.1\% \\ 
               & 50-59: & 11.5\% \\ 
               & 60-69: & 3.8\% \\ 
               & 70-79: & 1.0\% \\

        \hline
        Highest Education:  & Bachelor's degree:    & 51.0\% \\
                            & A-Level/O-Level:      & 18.3\% \\
                            & GCSE:                 & 15.4\%  \\
                            & Master's degree:      & 13.5\% \\ 
                            & PhD:                  & 1.9\% \\
        \hline

    \end{tabular}
    \caption{Participant demographics}
    \label{tab:exp1_demo}
\end{table}
\textbf{TODO: } Create some graphs off this data and put them in the appendix.

\begin{wrapfigure}{l}{6cm}
    \centering
    \begin{tabular}{|l|l|}
        \hline
        Metric & Average Rating \\
        \hline
        Leven     & 3.66 \\
        NYSIIS    & 2.92 \\
        Metaphone & 2.56 \\
        Phonetic Vec & 2.50 \\
        Soundex & 2.08 \\
        \hline
        Random  & 1.16 \\
        \hline
    \end{tabular}
    \caption{Average metric performance}
    \label{tab:exp1_results}
\end{wrapfigure}

Table \ref{tab:exp1_demo} contains the geographical breakdown of the participants assessed. As it can be seen over 60\% of participants can be considered highly educated (Bachelor’s and up). This is not fully reflective of the general population and therefore, has to be considered when interpreting the results. All participants were sourced from the US, this again requires consideration due to the large range of dialects present, that may bias the results. Further work could investigate the affect of location on these results.

Figure \ref{tab:exp1_results} shows the average results for the metrics

% 22 Missed values

% Results

@@

\section{Distribution of keys permutations (Vuln-keys)}

### 2019-08-05 Thesis/pages/implementation.tex
Changes; - Added implementation details - Added some results write ups for the first experiment

\section{GreenOnion}
Talk about the way a key is expanded and turned into a lot
of work for the kernel

>>>>

\section{GreenOnion}

\subsubsection{General design}
This section will discuss the overall technical implementation of GreenOnion alongside a deeper discussion into the unique aspect of the tool.

The tool starts by generating a 2048-bit RSA key through GPG\footnote{GNU Privacy Guard}. This key is then used to create a hash of all but the final block of the key. The final block of the key is left un-hashed due to the presence of the exponent ($e$). This exponent is incremented by one to provide a new key. This is the aspect provides rapid generation of unique key as work for the GPU. This prevents issues in such as entropy starvation when generating a large number of valid RSA keys. This produces valid keys but with abnormally large exponents, this was deemed as suitable due to the short term use-case for these keys. 3 bytes are used to represent the exponent giving the potential to create $2^{24} - 1$ extra keys for one expensive key generation.

All keys plus the intermediate hash are loaded on the GPU via an OpenCL kernel. This kernel is designed with hashing the final block, obtaining the final fingerprint and checking if the fingerprint is present in the provided list.

\subsubsection{Bloom filter}

Mass checking of fingerprints is the tools main functionality as it allows for millions of keys to be checked with a very small amount of overhead. This is achieved through the use of a bloom filter. A bloom filter is a probabilistic data structure that allows efficient checking for present of an element in a set. It is effectively a very large array of booleans that state wether an element is present. A position in the array is decided by a hashing algorithm. This is repeated a number of times with a number of hashing algorithms ($k$) to populate the array of length ($m$). This then means checking the presence of an element in the set will just mean hashing the target and checking the elements returned. This data structure therefore has a complexity of $O(k)$ regardless of the number of elements in the set.

However, due to the random distribution of the hashing algorithms commonly there is the possibility for collisions and, thus, the possibility of false-positives. The data structure also does not produce any false-negatives. This is fully suited to this use-case as any fingerprints tagged as ``possibility'' being present in the bloom filter can be followed up with a more expensive hash-table check to determine the actual presence. Therefore, if the levels of false-positives are controlled (by altering $k$ and $m$) the tool can search through huge number of potential keys without any decrease in speed.

\begin{figure}[h!]
    \centering
    \input{diagrams/bloom_filter.tex}
    \caption{Bloom filter example}
    \label{fig:bloom}
\end{figure}

Figure \ref{fig:bloom} shows the operation of a simple bloom filter. As it can be seen the element $n$ definitely does not exist in the set due to both array indices not being set. The performance boost when comparing large numbers of keys is substantial when compared to the similar tool Scallion mentioned in Section \ref{sec:greenDesign}. The results from the comparison will be quantified in Chapter \ref{cha:Experiments}.
